---
title: Creating Economic Tutorials with \faRProject \ and `learnr`
subtitle: Vanguard Scientific Instruments in Management\' 2023
author: Lyuben Ivanov, PhD
date: Sep 10, 2023
institute: Faculty of Economics and Business, Sofia University
output: binb::metropolis
fontsize: 12pt
header-includes:
  - \input{epigraph.tex}
  - \usepackage{fontawesome5}
  - \usepackage{graphicx}
editor_options: 
  markdown: 
    wrap: 72
---

```{r,setup, include = FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
options(digits = 2, scipen = 999)
library(vsim23)
```

# Introduction to `R`

## What is R?

\epigraph{\texttt{R} is a system for statistical computation and graphics.}{\texttt{R} Core Team}

`R` provides, among other things:

-   a programming language;

-   high level graphics;

-   interfaces to other languages;

-   debugging facilities.


## R Genealogy

```{r RhistoryFig, echo = FALSE, fig.height = 5.4, warning = FALSE}

rgen()

```


## The Birth of Scheme

\epigraph{Scheme, the dialect of Lisp that we use, is an attempt to bring together the power and elegance of Lisp and Algol. 
From Lisp we take the metalinguistic power that derives from the simple syntax, the uniform representation of programs as data objects, and the garbage-collected heap-allocation data.
From Algol we take lexical scoping and block structure, which are gifts from the pioneers of programming language design\ldots}{Abelson and Sussman}

## Design Principles of \texttt{R}

\epigraph{Everything that exists in \texttt{R} is an object.}{John M. Chambers}

\epigraph{Everything that happens in \texttt{R} is a function call.}{John M. Chambers}

\epigraph{Interfaces to other languages are a part of \texttt{R}.}{John M. Chambers}


# Introduction to `learnr`

## What is `learnr`?

`learnr` is an `R` package created and maintained by employees of Posit
(formerly RStudio).

It creates interactive tutorials using `R Markdown` and `Shiny`.

`learnr` uses a combination of:

-   narrative,

-   figures,

-   videos,

-   exercises,

-   and quizzes

to create self-paced tutorials for learning about `R` and `R` packages.

## RStudio/Posit: The Company Behind `learnr`!

```{r kableEx, warning = FALSE, echo = FALSE}
vsim23::top_downloads |>
  knitr::kable(caption = "Top 5 most downloaded packages in August 2023")
```

                   Source: https://cran.rstudio.com

## The Pillars of `learnr`

Developer interface (`R Studio` + `knitr` + `pandoc`):

-   `learnr` tutorials are built around R Markdown documents;
-   `shiny` inputs and outputs are components of HTML-based Rmd
    documents;
-   `shiny` apps are easily embedded in HTML-based Rmd documents;
-   `shiny` apps published on the web can also be included with
    `knitr::include_app()`.

Web interface (`shiny`):

-   use \faRProject functions to create HTML and CSS code;
-   publish tutorials on <https://shinyapps.io>, Shiny Server or Posit
    Connect.

# The Use of `learnr` Tutorials by Statisticans and Data Scientists

## The Use of `learnr` Over Time (Downloads per Year)

```{r packagepopularity, echo = FALSE, fig.height = 5.4, warning = FALSE}

vsim23::learnr_downloads |>
  dplyr::select(`annual downloads`) |>
  as.matrix() |>
  barplot(beside = TRUE, 
          names.arg = 2017:2023, 
          border = NA, 
          space = 0.5, 
          yaxt = "n", 
          col = gray.colors(7)
          )

axis(						                            # add y-axis to plot
  side = 2, 				                        # axis should be drawn on left side
  at = axTicks(2),
  las = 2,                        	      	# horizontal labels
  tick = F,				                          # remove ticks
  labels = axTicks(2) |> format(big.mark = ",")
)

abline(				    	
  h = axTicks(2),
  col = "white",	  	# specify color of horizontal lines
  lwd = 1		        	# specify horizontal lines width
  )
```



## `learnr` Tutorials Hosted in the Cloud

[**Posit Cloud Primers**](https://posit.cloud/learn/primers)

Twenty six `learnr` tutorials divided into 6 topics: 

-  The Basics;
-  Work with Data; 
-  Visualize Data; 
-  Tidy Your Data;
-  Iterate;
-  Write Functions.

## `learnr` Tutorials Hosted in the Cloud
\epigraph{\texttt{R} was written for statisticians, by statisticians.}{Marek Gagolewski}

[**OpenIntro::Introduction to Modern Statistics**](https://openintrostat.github.io/ims-tutorials/)

Six `learnr` tutorials, each of them corresponding to one part of the book and
comprised of multiple lessons for a total of 35 lessons that cover the entire
content of the book.

## `learnr` Tutorials Distrubuted as `R` Packages

\epigraph{When assigned 'R for Data Science'tudents should read the book and type in all the associated R commands themselves. Sadly, that never happens. These tutorials allow students to demonstrate (and their instructors to be sure) that all work has been completed.}{David Kane}

## `learnr` Tutorials Distrubuted as `R` Packages

[**Kane, D. (2023) r4ds.tutorials: Tutorials for 'R for Data Science'**](https://cran.r-project.org/package=r4ds.tutorials)

[**Kane, D. (2023) tidymodel.tutorials: Tutorials for 'Tidy Modeling with R'**](https://ppbds.github.io/tidymodels.tutorials/)

[**Kane, D. (2023) primer.tutorials: Tutorials for 'Primer for Bayesian Data Science'**](https://ppbds.github.io/primer.tutorials/)

[**Kane D (2023) tidycensus.tutorials: Tutorials for Analyzing US Census Data. **](https://ppbds.github.io/tidycensus.tutorials/)

# A Hands-on Experience with a Demo Tutorial Demonstrating How `learnr` Can Be Used for Teaching Economics

## Demo Tutorial

You can experiment with demo tutorial prepared for this conference by visiting

https://lyubenivanov.shinyapps.io/VSIM23demo

or by installing the package `vsim23` from \faGithub\ (https://github.com/lyuben-ivanov/vsim23)

and loading the tutorial with:

```
learnr::run_tutorial(
  name = "demo", 
  package = "vsim23"
  )
```
## Key Takeaways

Advantages of using `learnr` to create learning resources
\begin{itemize}
\item [{\faThumbsUp[regular]}] easy to create multiple similar questions by programming
\item [{\faThumbsUp[regular]}] uses \faRProject's powerful graphic and computation engines
\item [{\faThumbsUp[regular]}] facilitates cooperation due to strong \faGithub\ integration
\item [{\faThumbsUp[regular]}] easy to reuse own code and other people's code
\end{itemize}

Disadvantages of using `learnr` to create learning resources
\begin{itemize}
\item [{\faThumbsDown[regular]}] not very mature (current version is 0.11.4) 
\item [{\faThumbsDown[regular]}] much more suitable for formative rather than for summative assessment
\item [{\faThumbsDown[regular]}] not a learning management system (yet?)
\end{itemize}

## Questions? 

\begin{center} 
\resizebox{0.27\linewidth}{!}{\faQuestionCircle[regular]}
\end{center}

## Thank you! 

\begin{center} 
\resizebox{0.27\linewidth}{!}{\faGrin[regular]}
\end{center}






